### 2022-04-21 ms/ms.rmd
Realised that the dataset already had fixed names so removed redundant code here

#########################
## Phylogeny
#########################
 ## Tree data; also fix up some errors
    tree_data <-  data_long %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)

>>>>

#########################
## Phylogeny
#########################
 ## Tree data
    tree_data <-  data_long %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)
